Estimating duration using survival analysis

### 2024-03-12 cis-perfect-testing.tex
format equations better

Next, I derive $p_{ia}$.
By definition (see~\cpageref{perf-test:def:admissible}), we have, for any $i \in \set{D}$:
\begin{align}
p_{ia} &= \prob((b, e) \in \alpha_i \mid \theta) \\
\alpha_i &= \{ (b, e) : l_{j(i)}^{(b)} \leq b \leq r_{j(i)}^{(b)} \wedge l_{j(i)}^{(e)} \leq e \leq r_{j(i)}^{(e)}\}.
\intertext{Suppressing the conditioning on $\theta$, this gives:}
p_{ia}
&= \prob \left( l_{j(i)}^{(b)} \leq B_{j(i)} \leq r_{j(i)}^{(b)}, l_{j(i)}^{(e)} \leq E_{j(i)} \leq r_{j(i)}^{(e)} \right) \\
&= \prob \left( l_{j(i)}^{(e)} \leq E_{j(i)} \leq r_{j(i)}^{(e)} \mid l_{j(i)}^{(b)} \leq B_{j(i)} \leq r_{j(i)}^{(b)} \right) \prob \left( l_{j(i)}^{(b)} \leq B_{j(i)} \leq r_{j(i)}^{(b)} \right) \\
&=\sum_{b = l_{j(i)}^{(l)}}^{r_{j(i)}^{(b)}} \prob \left( l_{j(i)}^{(e)} \leq E_{j(i)} \leq r_{j(i)}^{(e)} \mid B_{j(i)} = b \right) \prob \left(B_{j(i)} = b \right) \\
&=\sum_{b = l_{j(i)}^{(b)}}^{r_{j(i)}^{(b)}} \prob \left( l_{j(i)}^{(e)} - b + 1 \leq D_{j(i)} \leq r_{j(i)}^{(e)} - b + 1 \right) \prob \left(B_{j(i)} = b \right) &\text{by def of $D_{j(i)}$} \\
&=\sum_{b = l_{j(i)}^{(b)}}^{r_{j(i)}^{(b)}} \left( S_\theta(l_{j(i)}^{(e)} - b + 1) - S_\theta(r_{j(i)}^{(e)} - b + 1) \right) \prob \left(B_{j(i)} = b \right) &\text{by def of $S_\theta$} \\
&\propto \sum_{b = l_{j(i)}^{(b)}}^{r_{j(i)}^{(b)}} \left( S_\theta(l_{j(i)}^{(e)} - b + 1) - S_\theta(r_{j(i)}^{(e)} - b + 1) \right)
\end{align}
under the assumption of uniform probability of infection time.

>>>>

Next, I derive $p_{ia}$.
By definition (see~\cpageref{perf-test:def:admissible}), we have, for any $i \in \set{D}$:
\begin{align}
p_{ia} =& \prob((b, e) \in \alpha_i \mid \theta) \\
\alpha_i =& \{ (b, e) : l_{j(i)}^{(b)} \leq b \leq r_{j(i)}^{(b)} \wedge l_{j(i)}^{(e)} \leq e \leq r_{j(i)}^{(e)}\}.
\intertext{Suppressing the conditioning on $\theta$, this gives:}
p_{ia}
=& \prob \left( l_{j(i)}^{(b)} \leq B_{j(i)} \leq r_{j(i)}^{(b)}, l_{j(i)}^{(e)} \leq E_{j(i)} \leq r_{j(i)}^{(e)} \right) \\
=& \prob \left( l_{j(i)}^{(e)} \leq E_{j(i)} \leq r_{j(i)}^{(e)} \mid l_{j(i)}^{(b)} \leq B_{j(i)} \leq r_{j(i)}^{(b)} \right) \\
   &\times\prob \left( l_{j(i)}^{(b)} \leq B_{j(i)} \leq r_{j(i)}^{(b)} \right) \\
=& \sum_{b = l_{j(i)}^{(l)}}^{r_{j(i)}^{(b)}} \prob \left( l_{j(i)}^{(e)} \leq E_{j(i)} \leq r_{j(i)}^{(e)} \mid B_{j(i)} = b \right) \prob \left(B_{j(i)} = b \right) \\
=& \sum_{b = l_{j(i)}^{(b)}}^{r_{j(i)}^{(b)}} \prob \left( l_{j(i)}^{(e)} - b + 1 \leq D_{j(i)} \leq r_{j(i)}^{(e)} - b + 1 \right) \prob \left(B_{j(i)} = b \right) &\text{by def of $D_{j(i)}$} \\
=& \sum_{b = l_{j(i)}^{(b)}}^{r_{j(i)}^{(b)}} \left( S_\theta(l_{j(i)}^{(e)} - b + 1) - S_\theta(r_{j(i)}^{(e)} - b + 1) \right) \prob \left(B_{j(i)} = b \right) &\text{by def of $S_\theta$} \\
\propto& \sum_{b = l_{j(i)}^{(b)}}^{r_{j(i)}^{(b)}} \left( S_\theta(l_{j(i)}^{(e)} - b + 1) - S_\theta(r_{j(i)}^{(e)} - b + 1) \right)
\end{align}
under the assumption of uniform probability of infection time.
